My title

### 2022-01-29 outputs/paper/paper.Rmd
upload

```{r}
final_graph <- 
  ggplot(cleaned_data, aes(Estimated_Dollar_Loss)) +
  facet_wrap(~Building_Status) +
  geom_histogram(binwidth = 10) +
  labs(x = "Estimated Dollar Loss",
       y = "Count")

final_graph
```

>>>>

```{r}
final_graph1 <- 
  cleaned_data %>%
  filter(Fire_Alarm_System_Operation == "1 - Fire alarm system operated") %>%
  ggplot(mapping = aes(x = Estimated_Dollar_Loss)) +
  geom_histogram(bins = 100) +
  xlim(0, 250000) +
  ylim(0, 250) +
  labs(x = "Estimated Dollar Loss",
       y = "Count")

final_graph2 <- 
  cleaned_data %>%
  filter(Fire_Alarm_System_Operation != "1 - Fire alarm system operated") %>%
  ggplot(mapping = aes(x = Estimated_Dollar_Loss)) +
  geom_histogram(bins = 100) +
  xlim(0, 250000) +
  ylim(0, 250) +
  labs(x = "Estimated Dollar Loss",
       y = "Count")

final_graph1
final_graph2
```
